%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Graduate Research Assistant} % Job title
    {Design, Innovation and Simulation Lab (DISL)} % Organization
    {The Ohio State University, Columbus, OH, USA} % Location
    {August 2017 --- Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Modeled, tested, and analyzed variable stiffness links (VSLs) for use in corobots.}
        \item{Developed software, planned, and conducted experiments for interdisciplinary research on attention to preview in human drivers.}
        \item{Mentored high school, undergraduate, and MS students on research projects.}
        \item{Administered and maintained lab server and rapid-prototyping equipment.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {REU Research Assistant} % Job title
    {NSF Interfaces and Surfaces REU} % Organization
    {Clemson University, Clemson, SC, USA} % Location
    {May 2016 --- August 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conducted numerical simulations of hydrogel membranses under illumination.}
        \item {Modeled and implemented code for numerical simulation of magnetically heated gels with cooling effects.}
        \item {Mentored incoming MS student on simulation software and high-performance-computing.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Undergraduate Research Assistant} % Job title
    {Biological Robotics at Tulsa Lab (BRAT Lab)} % Organization
    {The University of Tulsa, Tulsa, OK, USA} % Location
    {May 2015 --- July 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Pursued independent research on grasping and manipulation with quadruped robots.}
        \item {Developed method optimal foot-shuffle algorithm for quadruped stabilization under disturbances and body-position constraints.}
        \item {Developed interactive 3D model of quadruped kinematics and tip-over stability.}
      \end{cvitems}
    }

\end{cventries}