%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Graduate Research Assistant} % Job title
    {Design, Innovation and Simulation Lab (DISL)} % Organization
    {The Ohio State University, Columbus, OH} % Location
    {August 2017 --- Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Modeled, tested, and analyzed variable stiffness robotic arm links for use in physical human-robot interaction.}
        \item{Developed software for, planned, conducted, analyzed, and interpreted experiments for interdisciplinary research on attention to preview in human drivers.}
        \item{Mentored high school, undergraduate, and MS student research projects.}
        \item{Administered and maintained lab server and rapid-prototyping equipment.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {REU Research Assistant} % Job title
    {NSF Interfaces and Surfaces REU} % Organization
    {Clemson University, Clemson, SC} % Location
    {May 2016 --- August 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conducted numerical simulations of hydrogel membranes under illumination.}
        \item {Modeled and implemented code for numerical simulation of magnetically heated gels with cooling effects.}
        \item {Mentored incoming MS student on simulation software and high-performance-computing.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Undergraduate Research Assistant} % Job title
    {Biological Robotics at Tulsa Lab (BRAT Lab)} % Organization
    {The University of Tulsa, Tulsa, OK} % Location
    {May 2015 --- July 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Pursued independent research on grasping and manipulation with quadruped robots.}
        \item {Developed optimal foot-shuffle algorithm for quadruped stabilization under disturbances and body-position constraints.}
        \item {Developed interactive software to model quadruped kinematics and tip-over stability.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
{Mechanical Engineering Senior Project} % Job title
{The Tulsa Children's Museum} % Organization
{Tulsa, OK} % Location
{October 2016 --- May 2017} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item{Team designed and built a 15 foot steel auger ball-lift system for an exhibit at the children's museum.}
		\item{Elected project MVP. Our project was voted second best by our class.}
		\item{Video of the project before it was installed in the museum: \href{https://youtu.be/jlq1ikz-zHM}{\color{awesome} https://youtu.be/jlq1ikz-zHM}}
	\end{cvitems}
}

%---------------------------------------------------------
%\cventry
%{Student Grader} % Job title
%{The University of Tulsa Mechanical Engineering Department} % Organization
%{Tulsa, OK, USA} % Location
%{Spring 2016 --- Spring 2017} % Date(s)
%{
%	\begin{cvitems} % Description(s) of tasks/responsibilities
%		\item{Mechanics of Materials (ME 3023); Instrumentation and Measurement (ME 3053)}
%	\end{cvitems}
%}

%---------------------------------------------------------
\cventry
{Mechanical Engineering Intern} % Job title
{Burns and McDonnell --- Aviation and Federal Division} % Organization
{Kansas City, MO} % Location
{Summer 2015} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item{Assisted in designing HVAC and plumbing systems at Tinker Air Force Base, Portland International Airport, the Sampson School at Guantanamo Bay Naval Base, and the Kansas City National Security Campus.}
	\end{cvitems}
}

%---------------------------------------------------------
%\cventry
%{Jobsite Administrative Assistant} % Job title
%{Navitas ESCO} % Organization
%{Olathe, KS} % Location
%{Summer 2014} % Date(s)
%{}

%---------------------------------------------------------
%\cventry
%	{} % Job title
%	{Dairy Queen} % Organization
%	{Overland Park, KS} % Location
%	{2012 --- 2013} % Date(s)
%	{}

\end{cventries}